---
title: "Homework 1"
author: Fiona Ehrich
output: github_document
---

```{r libraries}
library(tidyverse)
library(palmerpenguins)
```

## Problem 1

#### Create a data frame with the specified elements.

```{r create_df}
prob1_df =
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
  )
```

#### Take the mean of each variable in my data frame.

```{r mean_pull_var}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

I can take the mean of numbers and logical but not character or factor.

#### Apply `as.numeric` to each variable.

```{r try_numeric, eval = FALSE}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```
Note: The output is not shown for the above code chunk per the assignment instructions.

`samp` stays the same as it was already numeric. `samp_gt_0` gets turned into 0s and 1s. `char_vec` just becomes a series of NAs. `factor_vec` becomes a collection of 1s, 2s, and 3s.

#### Apply the three specified manipulations to the logical vector.

```{r log_vec_manips}
as.numeric(pull(prob1_df, samp_gt_0)) * (pull(prob1_df, samp))
as.factor(pull(prob1_df, samp_gt_0)) * (pull(prob1_df, samp))
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * (pull(prob1_df, samp))
```

## Problem 2

#### Load `penguins` dataset.

```{r load_peng}
data("penguins", package = "palmerpenguins")
```

#### Description of `penguins` dataset.

```{r peng_summary}
names(penguins)
head(penguins)
dim(penguins)
summary(penguins)
```

In this dataset there are 8 variables - species, island, bill length, bill depth, flipper length, body mass, sex, and year. There are some missing values (NA's).

```{r peng_rows_cols}
nrow(penguins)
ncol(penguins)
```

There are 344 rows and 8 columns.

```{r peng_flip_leng_mean}
mean(pull(penguins, flipper_length_mm), na.rm = TRUE)
```

The mean flipper length is 200.9152 mm. This is also reflected in the prior table generated by `summary(penguins)`.

#### Generate and export scatterplot of `flipper_length_mm` (y) vs `bill_length_mm` (x).

```{r peng_scatterplot}
ggplot(penguins, aes(x = pull(penguins, bill_length_mm), y = pull(penguins, flipper_length_mm), color = pull(penguins, species))) + geom_point()
ggsave("scatter.plot.pdf", height = 4, width = 6)
```