---
title: "Homework 1"
author: Fiona Ehrich
output: github_document
---

```{r libraries}
library(tidyverse)
library(palmerpenguins)
```

## Problem 1

#### Create a data frame with the specified elements.

```{r create_df}
prob1_df =
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
  )
```

#### Take the mean of each variable in my data frame.

```{r mean_pull_var}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

I can take the mean of numbers and logical but not character or factor.

#### Apply `as.numeric` to each variable.

```{r try_numeric, eval = FALSE}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```
*Note: The output is not shown for the above code chunk per the assignment instructions.*

The numeric variable stays the same as it was already numeric. The logical variable gets turned into 1s and 0s (representing TRUE and FALSE). The character vector just becomes a series of NAs (not "translated" in any way into numeric values). The factor vector becomes a collection of 1s, 2s, and 3s (representing the three levels).

#### Apply the three specified manipulations to the logical vector.

```{r log_vec_manips}
as.numeric(pull(prob1_df, samp_gt_0)) * (pull(prob1_df, samp))
as.factor(pull(prob1_df, samp_gt_0)) * (pull(prob1_df, samp))
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * (pull(prob1_df, samp))
```

## Problem 2

#### Load `penguins` dataset.

```{r load_peng}
data("penguins", package = "palmerpenguins")
```

#### Description of `penguins` dataset.

In this dataset, the variables are: `r names(penguins)`.

The penguin species included are: `r levels(pull(penguins, species))`. The penguins are from the islands: `r levels(pull(penguins, island))`.

There are `r nrow(penguins)` rows and `r ncol(penguins)` columns.

The mean flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)` mm. The median weight of the penguins is `r median(pull(penguins, body_mass_g), na.rm = TRUE)` g (IQR `r IQR(pull(penguins, body_mass_g), na.rm = TRUE)`).

Displayed below are the first portion of the dataset, information on the structure of the dataset, and a high-level summary of the data. 

```{r peng_summary}
head(penguins)
str(penguins)
summary(penguins)
```

As indicated by the `summary(penguins)` output, there are some missing values (NA's) in this dataset.

#### Generate and export scatterplot of `flipper_length_mm` (y) vs `bill_length_mm` (x).

```{r peng_scatterplot}
ggplot(penguins, aes(x = pull(penguins, bill_length_mm), y = pull(penguins, flipper_length_mm), color = pull(penguins, species))) + geom_point()
ggsave("scatter.plot.pdf", height = 4, width = 6)
```